---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(tidymodels)
library(modelsummary)
library(nflverse)
```


# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....



# Data {#sec-data}



```{r}
#| echo: false
#| warning: false
#| message: false

nfl_2020 <- read_csv(here::here("data/analysis_data.csv"))
nfl_2020_train <- nfl_2020 |>
  filter(week<=9)
nfl_2020_test <- nfl_2020 |>
  filter(week>9)
```



```{r}
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of nfl"
#| echo: false

first_model_tidymodels <-
  linear_reg() |>
  set_engine(engine = "lm") |>
  fit(
    passing_epa ~ completions + attempts + passing_yards,
    data = nfl_2020_train
  )

second_model_tidymodels <-
  linear_reg() |>
  set_engine(engine = "lm") |>
  fit(
    passing_epa ~ completions + attempts + passing_yards + sacks,
    data = nfl_2020_train
  )

modelsummary(list("Model 1" = first_model_tidymodels,
                  "Model 2" = second_model_tidymodels))
```

Talk way more about it. 

```{r}
#| echo: false

predicted_results <- second_model_tidymodels |>
  predict(new_data = nfl_2020_test) |>
  cbind(nfl_2020_test) |>
  select(recent_team, week, passing_epa, .pred) |>
  arrange(recent_team,week) |>
  rename(predicted_passing_epa = .pred) 
```


# Model

The goal of our modelling strategy is twofold. Firstly,...

## Model set-up


\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \beta_0+\beta_1 x_{1i} + \beta_2 x_{2i}
\end{align}

where $y_i$ refers to the total expected points added on pass attempts and sacks of some individual $i$, $x_{1i}$ refers the number of completed passes of some individual $i$......

# Results

```{r}
predicted_results |>
  ggplot(aes(x= passing_epa, y= predicted_passing_epa)) + geom_point() +
  geom_abline(intercept = 0, slope = 1, color = "red") #diagonal line
```




# Discussion



\newpage



\newpage


# References


